Self Regulation Ontology Retest Analyses

### 2018-06-06 code/SRO_Retest_Analyses.Rmd
added lit ve emp measure plot

>>>>

```{r warning=FALSE, message=FALSE}
p1 = rel_comp %>%
  filter(task == 'task') %>%
ggplot(aes(x = var, y = retest_reliability)) + 
  geom_boxplot(fill='#00BFC4', position="identity")+
  geom_point(aes(x = var, y = mean_pearson),color="purple", fill="purple", size=3, shape=23)+
  coord_flip()+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.5, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80"),
        legend.position = 'bottom') + 
  xlab("")+
  ylab("")+
  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))

p2 = rel_comp %>%
  filter(task == 'survey') %>%
ggplot(aes(x = var, y = retest_reliability)) + 
  geom_boxplot(fill='#F8766D', position="identity")+
  geom_point(aes(x = var, y = mean_pearson),color="purple", fill="purple", size=3, shape=23)+
  coord_flip()+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.5, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80"),
        legend.position = 'bottom') + 
  xlab("")+
  ylab("")+
  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))

p3 <- arrangeGrob(p1, p2,nrow=1)

ggsave('LitVsEmp_Measure_Plot.jpg', plot = p3, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 24, height = 20, units = "in", dpi=100)
rm(p1, p2, p3)
```

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/LitVsEmp_Measure_Plot.jpg')
```
